Tempo Analysis: The Sound of Teaching Music 2

### 2021-06-20 experiment-2/analysis/stats/ioi.Rmd
tweak notes
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

2. Excluded participants
- SubNr 2: A deviated tempo
- SubNr 3: Insufficient motor skills

@@

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms)

@@

### Plot
#### Line graph
- Error bars show SEM of the mean
- A dashed line represents the tempo given by a metronome.

>>>>

2. Excluded participants
- SubNr 3: Insufficient motor skills

@@

@@

### Plot
#### Line graph
- Error bars show SEM of the mean.
- A dashed line represents the tempo given by a metronome.
